|

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
chore(manuscript): add cospar methods
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

## Cospar {#sec-methods-cospar}

We computed the
[Cospar `v0.1.9`](https://github.com/AllonKleinLab/cospar/releases/tag/v0.1.9) 
[@Wang2022-xb] fate potency score for the above processed multi-fate LARRY dataset, 
and selected the subset of the fate potency scores for evaluating bi-fate and 
uni-fate datasets. We used the following function calls to achieve this

```python
cospar.tmap.infer_Tmap_from_multitime_clones(
  adata_orig=adata, 
  compute_new=True,
  clonal_time_points=[2,4,6], 
  later_time_point=6,
  smooth_array=[20,15,10],
  sparsity_threshold=0.2, 
  max_iter_N=3
)
cospar.pl.fate_potency(
  adata=adata, 
  used_Tmap='transition_map',
  map_backward=True,
  method='norm-sum',
  color_bar=True,
  fate_count=True
)
```
